### 2019-10-17 README.Rmd
Added cuttoff argument to diffEnrich; updated README and vignette
Added arg checks to .data_read, and added get_kegg read = TRUE example to README and vignette

    kegg_to_pathway2019-04-26Release_90.0+_04-26_Apr_19.txt
    ncbi_to_kegg2019-04-26Release_90.0+_04-26_Apr_19.txt
    pathway_to_species2019-04-26Release_90.0+_04-26_Apr_19.txt

**Note:** Because it is assumed that the user might want to use the data sets generated by *get_kegg*, it is careful not to
overwrite data sets with exact names. *get_kegg* checks the path provided for data sets generated 'same-day/same-version', 
and if it finds even one of the three, it will not re-write any of the data sets. It will still however, let the user know
it is not writing out new data sets and still generate the named list object. Users can generate 'same-day/same-version'
data sets in different directories if they so choose.

@@

@@

```{r diffEnrich}
## Perform differential enrichment
diff_enrich <- diffEnrich(list1_pe = list1_pe, list2_pe = list2_pe, method = 'none') 
```

>>>>

    ncbi_to_kegg2019-10-17Release_92.0+_10-17_Oct_19.txt
    kegg_to_pathway2019-10-17Release_92.0+_10-17_Oct_19.txt
    pathway_to_species2019-10-17Release_92.0+_10-17_Oct_19.txt

**Note:** Because it is assumed that the user might want to use the data sets generated by *get_kegg*, it is careful not to
overwrite data sets with exact names. *get_kegg* checks the path provided for data sets generated 'same-day/same-version', 
and if it finds even one of the three, it will not re-write any of the data sets. It will still however, let the user know
it is not writing out new data sets and still generate the named list object. Users can generate 'same-day/same-version'
data sets in different directories if they so choose. Additionaly, *get_kegg* can be used to read in saved versions of the txt files
generated from a previous call (like those displayed above), and generate an R list object that is compatible with downstream
functions.

@@

```{r get_kegg_read, eval=FALSE}
## run get_kegg() using rat
kegg_rno <- get_kegg(read = TRUE, path = "/path/to/files", date = "2019-10-17", release = "92")
```

Here is an example of the output:

    Reading in the following files:
    ncbi_to_kegg2019-10-17Release_92.0+_10-17_Oct_19.txt
    kegg_to_pathway2019-10-17Release_92.0+_10-17_Oct_19.txt
    pathway_to_species2019-10-17Release_92.0+_10-17_Oct_19.txt
    File location: ~/Desktop

@@

```{r diffEnrich}
## Perform differential enrichment
diff_enrich <- diffEnrich(list1_pe = list1_pe, list2_pe = list2_pe, method = 'none', cutoff = 0.05) 
```
